Our peculiar motion across the Universe

### 2019-07-02 paper/main.tex
edit

\documentclass[onecolumn]{aastex62}
\submitjournal{ApJL}
\title{Our peculiar motion across the Universe}
\shortauthors{Forero-Romero}

@@

>>>>

\documentclass[onecolumn]{aastex62}
\submitjournal{ApJL}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc}\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc}\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\kms}{{\ifmmode{{\rm km\, {s}^{-1}}}\else{km s$^{-1}$}\fi}}

\title{Our peculiar motion across the Universe}
\shortauthors{Forero-Romero}

@@

\section{Numerical Setup}
We use simulations from the Abacus project \cite{abacus}.

We use the simulation boxes with size $L_{\rm box}=720$\hMpc simulated
with $1440^3$ particles and a resulting particle mass of $\sim 1\times
10^{10}$\hMpc. 
We use the set of 41 boxes with different $\omega$CDM cosmological
parameters which are phase-matched to isolate cosmology dependences.

\section{Sample Selection}

We select all halos with a maximum circular velocity larger than $xx$\kms.

\section{Results}

\section{Conclusions}
